---
title: "Developing Data Products Assignment 3"
author: "Siyang Ni"
date: "2023-05-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Assignment Instructions
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! Review criteria

The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?

Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

```{r, warning=FALSE, message=FALSE}
library(foreign)
library(plotly)
library(reshape2)
library(tidyverse)
library(tidymodels)
library(pastecs)
library(naniar)

df <- read.dta("mcs8156/mcs6_cm_interview.dta")
```

Here we will plot prediction of tips based on total bill paied using the built-in tips dataset in R.

```{r}
# recode
levels(df$FCCOMH00) <- c(-3, -2, -1, 0, 1, 2, 3, 4, 5, 6, 7, 8)

df$FCCOMH00[df$FCCOMH00 %in% c(-3, -2, -1)] <- NA
df$FCCOMH00 <- droplevels(df$FCCOMH00)

df$FCCOMH00 <- as.numeric(df$FCCOMH00)

# set x as hours polying video games during weekdays 
# and y as educational expectation
x <- df$FCCOMH00
y <- df$FCSTYU00

# Split the data
set.seed(123)
df_split <- initial_split(df)
df_training <- df_split %>% 
  training()
df_test <- df_split %>% 
  testing()

# fit the training the data to an OLS model
lm_model <- linear_reg() %>% 
  set_engine('lm') %>% 
  set_mode('regression') %>%
  fit(FCSTYU00 ~ FCCOMH00, data = df_training) 

# using the model to predict a randomly generated column of educational expectation
x_range <- seq(1, 8, length.out = 8)
x_range <- matrix(x_range, nrow=100, ncol=1)
xdf <- data.frame(x_range)
colnames(xdf) <- c('FCCOMH00')

ydf <- lm_model %>%
  predict(xdf) 

## generate the prediction matrix
colnames(ydf) <- c('FCSTYU00')
xy <- data.frame(xdf, ydf) 

# Plotting
fig <- plot_ly(data = df_training, x = ~FCCOMH00, y = ~FCSTYU00, type = 'scatter', name = 'train', mode = 'markers', alpha = 0.65) %>% 
  add_trace(data = df_test, x = ~FCCOMH00, y = ~FCSTYU00, type = 'scatter', name = 'test', mode = 'markers', alpha = 0.65 ) %>% 
  add_trace(data = xy, x = ~FCCOMH00, y = ~FCSTYU00, name = 'prediction', mode = 'lines', alpha = 1)
fig

 

```



